---
title: "R markdown test"
author: "BVD"
date: "9/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First we need to build the HLM models in R (done)
Then do the AIC testing (not possible. We'll do a simple variance explained argument)
Then do assumption checking
Then build descriptives for gain aggregated and disagregated and add the means to the descriptives table

---
title: "Equity analysis"
output: html_document
---

Load stuff (There are some packages that we don't need here, but I didn't clean them up. Sorry.)
```{r}
load("~/Box Sync/work/Research/R stuff/hmiout40") #Ben's computer
library("ggplot2")
library("HLMdiag")
library("DHARMa")
library("car") #for the Levene test which we will not discuss here
library("Matrix")
library(mitools)
library(stargazer)
library(lme4)
library(nlme)
library(mice)
library(mitml)
library(multcomp)
library(foreach)
library(ggplot2)
library(stringr)
library(dplyr)  #I load dplyr last because some of its functions (select) will be masked by plyr and it is a PITA to debug
```

Creating mitml and extra variables
```{r}
MIdata<-mids2mitml.list(hmi.out40)
MIdata <- within(MIdata,{
  G.pre <- clusterMeans(pre_scor,crse_id) # calculate group means
  stud_pre_cent <- pre_scor - G.pre          # center around group means
  class_pre_cent <- G.pre - mean(pre_scor)
  collabnla <- ifelse(colablrn==1,ifelse(used_las==0,1,0),0)
  gain <- pst_scor - pre_scor
})
```

Models (Note, we can't actually use these since they don't work with the with function)
```{r}
mod1 <- (gain~1 + (1|crse_id))
mod2 <- (gain~1 + used_las + collabnla + (1|crse_id))
mod3 <- (gain~1 + stud_pre_cent+  used_las + collabnla + (1|crse_id))
mod4 <- (gain~1 + stud_pre_cent+  used_las + collabnla + (1+ stud_pre_cent|crse_id))
mod5 <- (gain~1 + stud_pre_cent+  used_las + collabnla + class_pre_cent + (1|crse_id))
mod6 <- (gain~1 + stud_pre_cent+  used_las + collabnla + class_pre_cent + (1+ stud_pre_cent|crse_id))
```

Run HLM models
```{r}
HLM1<-with(MIdata,{lmer(gain~1 + (1|crse_id))})
HLM2<-with(MIdata,{lmer(gain~1 + used_las + collabnla + (1|crse_id))})
HLM3<-with(MIdata,{lmer(gain~1 + stud_pre_cent+  used_las + collabnla + (1|crse_id))})
HLM4<-with(MIdata,{lmer(gain~1 + stud_pre_cent+  used_las + collabnla + (1+ stud_pre_cent|crse_id))})
HLM5<-with(MIdata,{lmer(gain~1 + stud_pre_cent+  used_las + collabnla + class_pre_cent + (1|crse_id))})
HLM6<-with(MIdata,{lmer(gain~1 + stud_pre_cent+  used_las + collabnla + class_pre_cent + (1+ stud_pre_cent|crse_id))})
```

Run MLR models
```{r}
MLR1<-with(MIdata,{lm(gain~1)})
MLR2<-with(MIdata,{lm(gain~1 + used_las + collabnla)})
MLR3<-with(MIdata,{lm(gain~1 + stud_pre_cent+  used_las + collabnla)})
MLR4<-with(MIdata,{lm(gain~1 + stud_pre_cent+  used_las + collabnla)})
MLR5<-with(MIdata,{lm(gain~1 + stud_pre_cent+  used_las + collabnla + class_pre_cent)})
MLR6<-with(MIdata,{lm(gain~1 + stud_pre_cent+  used_las + collabnla + class_pre_cent)})
```

HLM Model outputs
```{r}
testEstimates(HLM1, var.comp=TRUE)
testEstimates(HLM2, var.comp=TRUE)
testEstimates(HLM3, var.comp=TRUE)
testEstimates(HLM4, var.comp=TRUE)
testEstimates(HLM5, var.comp=TRUE)
testEstimates(HLM6, var.comp=TRUE)
```

MLR Model outputs
```{r}
testEstimates(MLR1, var.comp=TRUE)
testEstimates(MLR2, var.comp=TRUE)
testEstimates(MLR3, var.comp=TRUE)
testEstimates(MLR4, var.comp=TRUE)
testEstimates(MLR5, var.comp=TRUE)
testEstimates(MLR6, var.comp=TRUE)
```

Assumption checking as recommended here: https://ademos.people.uic.edu/Chapter18.html
```{r}
sum1<-within(MIdata,{summary(gain1)})
sum1
```



Creating groups for final model
```{r}
WM=c(1,0,0,0,0,0,0,0,0,0,0,0,0)
WMC=c(1,0,1,0,0,0,0,0,0,0,0,0,0)
WMLA=c(1,0,0,1,0,0,0,0,0,0,0,0,0)
BM=c(1,0,0,0,0,1,0,0,0,0,0,0,0)
BMC=c(1,0,1,0,0,1,0,0,0,0,1,0,0)
BMLA=c(1,0,0,1,0,1,0,0,0,1,0,0,0)
WF=c(1,0,0,0,0,0,1,0,0,0,0,0,0)
WFC=c(1,0,1,0,0,0,1,0,0,0,0,0,1)
WFLA=c(1,0,0,1,0,0,1,0,0,0,0,1,0)
BF=c(1,0,0,0,0,1,1,0,0,0,0,0,0)
BFC=c(1,0,1,0,0,1,1,0,0,0,1,0,1)
BFLA=c(1,0,0,1,0,1,1,0,0,1,0,1,0)

contrast.formulas <-rbind('White Male'=WM, 'White Male Collab'=WMC, 'White Male LA'=WMLA,
                          'Black Male'=BM, 'Black Male Collab'=BMC, 'Black Male LA'=BMLA,
                          'White Female'=WF,'White Female Collab'=WFC, 'White Female LA'=WFLA,
                          'Black Female'=BF,'Black Female Collab'=BFC, 'Black Female LA'=BFLA)
```

Confidence interval for MI attempt (This is where I'm stuck)
```{r}
get.est <- foreach(i=1:10, .combine=rbind) %do% {
  sxp3 <- summary(glht(post3[[i]], linfct=contrast.formulas)) #specifically for post3
  covp3 <- vcov(glht(post3[[i]], linfct=contrast.formulas))
  data.frame(imp=i, 
             group=rownames(sx$linfct),
             d = sxp3$test$coefficients, 
             var.d = sxp3$test$sigma,
             cov = covp3)
}


p3est <- get.est %>% group_by(group) %>% 
                  summarise(Q = mean(d), 
                            U = mean(var.d), 
                            B = var(d), 
                            T = U + (1+1/max(imp)*B), 
                            LCL = Q - 1.96*sqrt(T), 
                            UCL = Q + 1.96*sqrt(T),
                            SE = sqrt(T)) 

p3est

get.est <- foreach(i=1:10, .combine=rbind) %do% {
  sxp3 <- summary(glht(gain3[[i]], linfct=contrast.formulas)) #specifically for post3
  covp3 <- vcov(glht(gain3[[i]], linfct=contrast.formulas))
  data.frame(imp=i, 
             group=rownames(sx$linfct),
             d = sxp3$test$coefficients, 
             var.d = sxp3$test$sigma,
             cov = covp3)
}


g3est <- get.est %>% group_by(group) %>% 
                  summarise(Q = mean(d), 
                            U = mean(var.d), 
                            B = var(d), 
                            T = U + (1+1/max(imp)*B), 
                            LCL = Q - 1.96*sqrt(T), 
                            UCL = Q + 1.96*sqrt(T),
                            SE = sqrt(T),
                            cvwm = mean(cov.White.Male)) 

g3est
```

Ratios against majority
```{r}
ratmBF = g3est$Q[1]/g3est$Q[10]
ratmBFC = g3est$Q[2]/g3est$Q[11]
ratmBFL = g3est$Q[3]/g3est$Q[12]
ratmBM = g3est$Q[4]/g3est$Q[10]
ratmBMC = g3est$Q[5]/g3est$Q[11]
ratmBML = g3est$Q[6]/g3est$Q[12]
ratmWF = g3est$Q[7]/g3est$Q[10]
ratmWFC = g3est$Q[8]/g3est$Q[11]
ratmWFL = g3est$Q[9]/g3est$Q[12]


s.e.ratmBF = sqrt((ratmBF)^2*((g3est$T[1])/(g3est$Q[1]^2)+(g3est$T[10])/(g3est$Q[10]^2)-2*(g3est$cvwm[1]/((g3est$Q[1])*(g3est$Q[10])))))
s.e.ratmBFC = sqrt((ratmBFC)^2*((g3est$T[2])/(g3est$Q[2]^2)+(g3est$T[11])/(g3est$Q[11]^2)-2*(g3est$cvwm[2]/((g3est$Q[2])*(g3est$Q[11])))))
s.e.ratmBFL = sqrt((ratmBFL)^2*((g3est$T[3])/(g3est$Q[3]^2)+(g3est$T[12])/(g3est$Q[12]^2)-2*(g3est$cvwm[3]/((g3est$Q[3])*(g3est$Q[12])))))
s.e.ratmBM = sqrt((ratmBM)^2*((g3est$T[4])/(g3est$Q[4]^2)+(g3est$T[10])/(g3est$Q[10]^2)-2*(g3est$cvwm[4]/((g3est$Q[4])*(g3est$Q[10])))))
s.e.ratmBMC = sqrt((ratmBMC)^2*((g3est$T[5])/(g3est$Q[5]^2)+(g3est$T[11])/(g3est$Q[11]^2)-2*(g3est$cvwm[5]/((g3est$Q[5])*(g3est$Q[11])))))
s.e.ratmBML = sqrt((ratmBML)^2*((g3est$T[6])/(g3est$Q[6]^2)+(g3est$T[12])/(g3est$Q[12]^2)-2*(g3est$cvwm[6]/((g3est$Q[6])*(g3est$Q[12])))))
s.e.ratmWF = sqrt((ratmWF)^2*((g3est$T[7])/(g3est$Q[7]^2)+(g3est$T[10])/(g3est$Q[10]^2)-2*(g3est$cvwm[7]/((g3est$Q[7])*(g3est$Q[10])))))
s.e.ratmWFC = sqrt((ratmWFC)^2*((g3est$T[8])/(g3est$Q[8]^2)+(g3est$T[11])/(g3est$Q[11]^2)-2*(g3est$cvwm[8]/((g3est$Q[8])*(g3est$Q[11])))))
s.e.ratmWFL = sqrt((ratmWFL)^2*((g3est$T[9])/(g3est$Q[9]^2)+(g3est$T[12])/(g3est$Q[12]^2)-2*(g3est$cvwm[9]/((g3est$Q[9])*(g3est$Q[12])))))

s.e.ratmBF
s.e.ratmBFC
s.e.ratmBFL
s.e.ratmBM
s.e.ratmBMC
s.e.ratmBML
s.e.ratmWF
s.e.ratmWFC
s.e.ratmWFL
ratmBF
ratmBFC
ratmBFL 
ratmBM
ratmBMC
ratmBML
ratmWF
ratmWFC
ratmWFL
```
Ratios against self
```{r}
ratsBFC = g3est$Q[2]/g3est$Q[1]
ratsBFL = g3est$Q[3]/g3est$Q[1]
ratsBMC = g3est$Q[5]/g3est$Q[4]
ratsBML = g3est$Q[6]/g3est$Q[4]
ratsWFC = g3est$Q[8]/g3est$Q[7]
ratsWFL = g3est$Q[9]/g3est$Q[7]
ratsWMC = g3est$Q[11]/g3est$Q[10]
ratsWML = g3est$Q[12]/g3est$Q[10]

s.e.ratsBF = sqrt((ratsBF)^2*((g3est$T[2])/(g3est$Q[2]^2)+(g3est$T[1])/(g3est$Q[1]^2)-2*(g3est$cvwm[1]/((g3est$Q[1])*(g3est$Q[10]))))) #This doesn't work becuse I have to update the cvwm factor. 

ratsBFC
ratsBFL 
ratsBMC
ratsBML
ratsWFC
ratsWFL
ratsWMC
ratsWML
```

